\section*{Acknowledgements}

I would like to thank my supervisor Dr. Cecilia Mattevi for enormous amount of help, guidance, support and patience throughout my entire time in her group. 

I would also like to acknowledge the examiners, Prof. Alexander Tartakovskii and Dr Peter Petrov for reviewing this thesis.

Thank you to Dr Francesco Reale for all the talks, both serious and lighthearted, and for providing me with all the CVD samples, XRD, SEM and AFM measurements and analysis.

Thank you to Ms Maria Sokolikova for the enlightening conversations and cheering me on to finish this thesis, and for all the colloidal synthesis samples, TEM imaging and analysis.

Thank you to Dr Peter Sherrell, Dr Federico Pesci and Dr Sharda Kanudha for all the guidance and help with setting up experiments and support, and for heterostructure samples, SEM imaging, electrical measurements and analysis.

I would like to acknowledge the help from collaborators, Dr. Iddo Amit, Prof. Monica F. Craciun and Prof. Saverio Russo for performing the electrical measurements.

Thank you to all the lab and office mates, Chiara Grotta, Cong Lu, Aleksandra Krajewska, Julian Buchinger, Jerome Nicolas, Nikesh Patel, Elisa Burbaum, Jeremy Tan, Mauro Och, Apostolos Panagiotopoulos, Gang Cheng, Giulia Zemignani, Stefano Tagliaferri, Gianmaria Matrone, David Poussin, Shengyang Chen, Luca Occhi, Francesco Salerno, Bartosz Barzdajn for all the interactions, talks and support that made this PhD journey complete.

And finally a thank you to my family, mamie, tacie, bratu i bratowej, for all the love and support, dzi\k{e}kuj\k{e}.